Estimating the association between Facebook adoption and well-being in 72 countries

### 2023-02-06 ms.Rmd
Save intermediates for submission

keywords: well-being, social media
wordcount: "`r wordcountaddin:::word_count(filename = 'ms.Rmd')`"
bibliography: "references.bib"
floatsintext: yesnc
linenumbers: yes
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
header-includes:
  - |
    \setlength{\parskip}{0pt}
    \setlength\parindent{24pt}
csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: doc
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
always_allow_html: true
---

@@

((p_a / p_b) &
    theme(
      strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
      strip.text.y = element_text(margin = margin(0,2,0,2, "pt")),
      text = element_text(size = 7)
    )) +
  plot_layout(heights = c(4, 6)) +
  plot_annotation(tag_levels = "A")
```

@@

tmp %>%
  ggplot() +
  aes(
    x = Mean, 
    y = fct_rev(country), 
    col = Age, 
    fill = interaction(Age, cred, sep = " "), 
    shape = Sex
  ) +
  scale_y_discrete(
    "Country",
    expand = expansion(.015),
    labels = ~str_replace(., "World", "Average")
  ) +
  scale_x_continuous(
    str_glue(
      "Association with per capita Facebook users (95%CI)")
    ,
    breaks = extended_breaks(7),
    expand = expansion(.1)
  ) +
  scale_shape_manual(
    values = c(21, 22)
  ) +
  scale_color_brewer(
    "Age", palette = "Set1", aesthetics = c("color")
  ) +
  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
  geom_vline(xintercept = 0, lty = 2, linewidth = .25, col = "grey50") +
  geom_linerangeh(
    aes(xmin = CI_low, xmax = CI_high),
    size = .15, position = position_dodge2v(.7), 
    show.legend = FALSE
  ) +
  geom_point(
    size = .65, stroke = .45,
    position = position_dodge2v(.7)
  ) +
  facet_nested(
    ~ predictor + outcome, scales = "free_x",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  guides(
    fill = "none",
    color = guide_legend(override.aes = list(size = 1.5)),
    shape = guide_legend(override.aes = list(size = 1.5))
  ) +
  theme(
    text = element_text(size = 9),
    axis.text.y = element_text(size = rel(0.9), vjust = 0.35),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.y = element_blank(),
    panel.grid.major = element_line(
      size = .1, linetype = 2, color = "gray60"
    ),
    legend.position = "bottom", 
    legend.title = element_blank(),
    legend.box.margin = margin(-10, 0, -5, 0, "pt")
  )
```

@@

tmp %>%
  ggplot() +
  aes(
    x = Mean, 
    y = fct_rev(country), 
    col = Age, 
    fill = interaction(Age, cred, sep = " "), 
    shape = Sex
  ) +
  scale_y_discrete(
    "Country",
    expand = expansion(.015),
    labels = ~str_replace(., "World", "Average")
  ) +
  scale_x_continuous(
    str_glue(
      "Association with per capita Facebook users (95%CI)")
    ,
    breaks = extended_breaks(7),
    expand = expansion(.1)
  ) +
  scale_shape_manual(
    values = c(21, 22)
  ) +
  scale_color_brewer(
    "Age", palette = "Set1", aesthetics = c("color")
  ) +
  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
  geom_linerangeh(
    aes(xmin = CI_low, xmax = CI_high),
    size = .15, position = position_dodge2v(.7), 
    show.legend = FALSE
  ) +
  geom_point(
    size = .65, stroke = .45,
    position = position_dodge2v(.7)
  ) +
  facet_nested(
    ~ predictor + outcome, scales = "free_x",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  guides(
    fill = "none",
    color = guide_legend(override.aes = list(size = 1.5)),
    shape = guide_legend(override.aes = list(size = 1.5))
  ) +
  theme(
    text = element_text(size = 9),
    axis.text.y = element_text(size = rel(0.8), vjust = 0.35),
    axis.text.x = element_text(size = rel(0.9)),
    axis.title.y = element_blank(),
    panel.grid.major = element_line(
      size = .1, linetype = 2, color = "gray60"
    ),
    legend.position = "bottom", 
    legend.title = element_blank(),
    legend.box.margin = margin(-10, 0, -5, 0, "pt")
  )
```

>>>>

keywords: well-being, social media
wordcount: "`r wordcountaddin:::word_count(filename = 'ms.Rmd')`"
bibliography: "references.bib"
floatsintext: yesnc
linenumbers: yes
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
header-includes:
  - |
    \setlength{\parskip}{0pt}
    \setlength\parindent{24pt}
csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: doc
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: true
  papaja::apa6_docx: 
    number_sections: false
always_allow_html: true
---

@@

((p_a / p_b) &
    theme(
      strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
      strip.text.y = element_text(margin = margin(0,2,0,2, "pt")),
      text = element_text(size = 7)
    )) +
  plot_layout(heights = c(4, 6)) +
  plot_annotation(tag_levels = "A")
ggsave("Figure-1.pdf", width = 7, height = 6, dpi = 300)
```

@@

tmp %>%
  ggplot() +
  aes(
    x = Mean, 
    y = fct_rev(country), 
    col = Age, 
    fill = interaction(Age, cred, sep = " "), 
    shape = Sex
  ) +
  scale_y_discrete(
    "Country",
    expand = expansion(.015),
    labels = ~str_replace(., "World", "Average")
  ) +
  scale_x_continuous(
    str_glue(
      "Association with per capita Facebook users (95%CI)")
    ,
    breaks = extended_breaks(7),
    expand = expansion(.1)
  ) +
  scale_shape_manual(
    values = c(21, 22)
  ) +
  scale_color_brewer(
    "Age", palette = "Set1", aesthetics = c("color")
  ) +
  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
  geom_vline(xintercept = 0, lty = 2, linewidth = .25, col = "grey50") +
  geom_linerangeh(
    aes(xmin = CI_low, xmax = CI_high),
    size = .15, position = position_dodge2v(.7), 
    show.legend = FALSE
  ) +
  geom_point(
    size = .65, stroke = .45,
    position = position_dodge2v(.7)
  ) +
  facet_nested(
    ~ predictor + outcome, scales = "free_x",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  guides(
    fill = "none",
    color = guide_legend(override.aes = list(size = 1.5)),
    shape = guide_legend(override.aes = list(size = 1.5))
  ) +
  theme(
    text = element_text(size = 9),
    axis.text.y = element_text(size = rel(0.9), vjust = 0.35),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.y = element_blank(),
    panel.grid.major = element_line(
      size = .1, linetype = 2, color = "gray60"
    ),
    legend.position = "bottom", 
    legend.title = element_blank(),
    legend.box.margin = margin(-10, 0, -5, 0, "pt")
  )
ggsave("Figure-2.pdf", width = 7.2, height = 7.8, dpi = 300)
```

@@

tmp %>%
  ggplot() +
  aes(
    x = Mean, 
    y = fct_rev(country), 
    col = Age, 
    fill = interaction(Age, cred, sep = " "), 
    shape = Sex
  ) +
  scale_y_discrete(
    "Country",
    expand = expansion(.015),
    labels = ~str_replace(., "World", "Average")
  ) +
  scale_x_continuous(
    str_glue(
      "Association with per capita Facebook users (95%CI)")
    ,
    breaks = extended_breaks(7),
    expand = expansion(.1)
  ) +
  scale_shape_manual(
    values = c(21, 22)
  ) +
  scale_color_brewer(
    "Age", palette = "Set1", aesthetics = c("color")
  ) +
  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
  geom_linerangeh(
    aes(xmin = CI_low, xmax = CI_high),
    size = .15, position = position_dodge2v(.7), 
    show.legend = FALSE
  ) +
  geom_point(
    size = .65, stroke = .45,
    position = position_dodge2v(.7)
  ) +
  facet_nested(
    ~ predictor + outcome, scales = "free_x",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  guides(
    fill = "none",
    color = guide_legend(override.aes = list(size = 1.5)),
    shape = guide_legend(override.aes = list(size = 1.5))
  ) +
  theme(
    text = element_text(size = 9),
    axis.text.y = element_text(size = rel(0.8), vjust = 0.35),
    axis.text.x = element_text(size = rel(0.9)),
    axis.title.y = element_blank(),
    panel.grid.major = element_line(
      size = .1, linetype = 2, color = "gray60"
    ),
    legend.position = "bottom", 
    legend.title = element_blank(),
    legend.box.margin = margin(-10, 0, -5, 0, "pt")
  )
ggsave("Figure-A1.pdf", width = 7.2, height = 7.8, dpi = 300)
```
